Resilience and Home-Space for WSTS \thanks{This work was partly done while the author was supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-08-31 appendixPN.tex
section

 \begin{center}
	\begin{figure}
\includegraphics[width=0.75\textwidth]{FigurePN}
\caption{Construction of $N_2$ from $N_1$. Places are represented using circles, transitions are represented using lines. Arcs are represented by $\rightarrow$ and reset-arcs by $\arrowcircle$. Note that since the construction of $N_2$ from $N_1$ do not add new reset-arcs, the only reset-arcs in $N_2$ are the ones inherited from $N_1$.}
	\end{figure}
\end{center}

@@

>>>>

 \begin{center}
	\begin{figure}
\includegraphics[width=0.75\textwidth]{FigurePN}
\caption{Construction of $N_2$ from $N_1$.}
%			As usual, places are represented by circles, transitions by lines. Arcs are represented by $\rightarrow$.
%			and reset-arcs by $\arrowcircle$. 
%		Note that $N_2$ do not contain new reset-arcs that were not in $N_1$.}
%		the only reset-arcs in $N_2$ are the ones inherited from $N_1$.}
	\end{figure}
\end{center}

@@

\alain{dans le dessin Fig 2, écrire reset Petri net $N_1$ et pas Petri net}
